\pkg{RProtoBuf}: Efficient Cross-Language Data Serialization in R

### 2014-01-14 papers/jss/article.Rnw
Correct a typo: s/at time/at times/
Implement some suggestions from Karl:
* Improve the sentence comparing to Rserve
* Add more context about the structure of the protocol buffer schema.
  Section 2 is very high level / abstract, then section 3 dives into the
  R interface without ever describing field types, tag numbers, etc.
  Added three sentences or so to the beginning of section 3 before
  diving into the R examples.



git-svn-id: svn://svn.r-forge.r-project.org/svnroot/rprotobuf@773 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

%% TODO(de,ms)  What follows is oooooold and was lifted from the webpage
%%              Rewrite?
Protocol Buffers can be described as a modern, language-neutral, platform-neutral,
extensible mechanism for sharing and storing structured data.  Since their
introduction, Protocol Buffers have been widely adopted in industry with
applications as varied as %database-internal messaging (Drizzle), % DE: citation?
Sony Playstations, Twitter, Google Search, Hadoop, and Open Street Map.  
% TODO(DE): This either needs a citation, or remove the name drop
While traditional IDLs have at time been criticized for code bloat and
complexity, Protocol Buffers are based on a simple list and records
model that is compartively flexible and simple to use.

@@

Figure~\ref{fig:protobuf-distributed-usecase} illustrates an example
communication workflow with Protocol Buffers and an interactive R session.
Common use cases include populating a request remote-procedure call (RPC)
Protocol Buffer in R that is then serialized and sent over the network to a
remote server.  The server would then deserialize the message, act on the
request, and respond with a new Protocol Buffer over the network. The key
difference to, say, a request to an Rserve instance is that the remote server
may not even know the R language.

@@

For added speed and efficiency, the C++, Java, and Python bindings to
Protocol Buffers are used with a compiler that translates a Protocol
Buffer schema description file (ending in \texttt{.proto}) into
language-specific classes that can be used to create, read, write and
manipulate Protocol Buffer messages.  The R interface, in contrast,
uses a reflection-based API that is particularly well-suited for
interactive data analysis.  All messages in R have a single class
structure, but different accessor methods are created at runtime based
on the name fields of the specified message type.

@@

Table~\ref{tab:proto} shows an example \texttt{.proto} file which
defines the \texttt{tutorial.Person} type.  The R code in the right
column shows an example of creating a new message of this type and
populating its fields.

@@

To create or parse a Protocol Buffer Message, one must first read in 
the message type specification from a \texttt{.proto} file. The 
\texttt{.proto} files are imported using the \code{readProtoFiles}
function, which can either import a single file, all files in a directory,
or every \texttt{.proto} file provided by a particular R package.
The \texttt{.proto} file syntax for defining the structure of protocol
buffer data is described comprehensively on Google Code\footnote{See 
\url{http://code.google.com/apis/protocolbuffers/docs/proto.html}.}.

>>>>

%% TODO(de,ms)  What follows is oooooold and was lifted from the webpage
%%              Rewrite?
Protocol Buffers can be described as a modern, language-neutral, platform-neutral,
extensible mechanism for sharing and storing structured data.  Since their
introduction, Protocol Buffers have been widely adopted in industry with
applications as varied as %database-internal messaging (Drizzle), % DE: citation?
Sony Playstations, Twitter, Google Search, Hadoop, and Open Street Map.  
% TODO(DE): This either needs a citation, or remove the name drop
% MS: These are mostly from blog posts, I can't find a good reference
% that has a long list, and the name and year citation style seems
% less conducive to long lists of marginal citations like blog posts
% compared to say concise CS/math style citations [3,4,5,6]. Thoughts?
While traditional IDLs have at times been criticized for code bloat and
complexity, Protocol Buffers are based on a simple list and records
model that is compartively flexible and simple to use.

@@

Figure~\ref{fig:protobuf-distributed-usecase} illustrates an example
communication workflow with Protocol Buffers and an interactive R session.
Common use cases include populating a request remote-procedure call (RPC)
Protocol Buffer in R that is then serialized and sent over the network to a
remote server.  The server would then deserialize the message, act on the
request, and respond with a new Protocol Buffer over the network. 
The key difference to, say, a request to an Rserve instance is that
the remote server may be implemented in any language, with no
dependence on R.

@@

For added speed and efficiency, the C++, Java, and Python bindings to
Protocol Buffers are used with a compiler that translates a Protocol
Buffer schema description file (ending in \texttt{.proto}) into
language-specific classes that can be used to create, read, write and
manipulate Protocol Buffer messages.  The R interface, in contrast,
uses a reflection-based API that is particularly well-suited for
interactive data analysis.  
All messages in R have a single class
structure, but different accessor methods are created at runtime based
on the named fields of the specified message type.

@@

Table~\ref{tab:proto} shows an example \texttt{.proto} file which
defines the \texttt{tutorial.Person} type.  The R code in the right
column shows an example of creating a new message of this type and
populating its fields.  A \texttt{.proto} file may contain one or more
message types, and each message type has one or more fields.  A field
is specified with a unique number, a name, a value type, and a field
rule specifying whether the field is optional, required, or repeated.
The supported value types are numbers, enumerations, booleans,
strings, raw bytes, or other nested message types.
The \texttt{.proto} file syntax for defining the structure of protocol
buffer data is described comprehensively on Google Code\footnote{See 
\url{http://code.google.com/apis/protocolbuffers/docs/proto.html}.}.

@@

To create or parse a Protocol Buffer Message, one must first read in 
the message type specification from a \texttt{.proto} file. The 
\texttt{.proto} files are imported using the \code{readProtoFiles}
function, which can either import a single file, all files in a directory,
or every \texttt{.proto} file provided by a particular R package.
